An indexed construction of semi-cubical types

### 2021-06-30 paper/paper.tex
One other fix of indices for r

\begin{figure*}
  \centerline{ \framebox{$
        \begin{array}{llcl}
          \cohbox{l,\epsilon,\epsilon',q,r}{\!\!\!\begin{array}{l}n,p\\\mbox{}[p \leq r \leq q \leq n - 2]\end{array}}    & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\end{array} & :      & \!\!\!\begin{array}{ll}\downbox{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\epsilon',r}{n,p}(D)(d)) \\ \eqett \downbox{l,\epsilon',r-1}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))\end{array}                                                                             \\
          \cohbox{l,\epsilon,\epsilon',q,r}{n,0}                                & D~\unitpoint                     & \defeq & \reflett(\unitpoint)                                                                                         \\
          \cohbox{l,\epsilon,\epsilon',q,r}{n,p'+1}                             & D~(d,b)                          & \defeq & (\cohbox{l,\epsilon,\epsilon',q,r}{n,p'}(D)(d),\cohlayer{l,\epsilon,\epsilon',q,r}{n,p'}(D)(d)(b))           \\
          \\
          \cohlayer{l,\epsilon,\epsilon',q,r}{\!\!\!\begin{array}{l}n,p\\\mbox{}[p < r \leq q \leq n - 2]\end{array}} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\\(b:\mylayer{l}^{n,p}(D)(d))\end{array} & :      & \!\!\!\begin{array}{ll}\downlayer{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\epsilon',r}{n,p}(D)(d))(\downlayer{l,\epsilon',r}{n,p}(D)(d)(b)) \\ \eqett \downlayer{l,\epsilon',r}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))(\downlayer{l,\epsilon,q+1}{n,p}(D)(d)(b))\end{array}                                                                             \\
          \cohlayer{l,\epsilon,\epsilon',q,r}{n,p}                              & D~d~c                            & \defeq & \!\!\begin{array}{l}(\cohcube{l,\epsilon,\epsilon',q-1,r-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d))(c_L),\\\;\cohcube{l,\epsilon,\epsilon',q-1,r-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))(c_R))\end{array}                                                                               \\
          \\
          \cohcube{l,\epsilon,\epsilon',q,r}{\!\!\!\begin{array}{l}n,p\\\mbox{}[p \leq r \leq q \leq n - 2]\end{array}}  & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(E:\mycubsetcomp{l}{n}(D))\\(d:\mybox{l}^{n,p}(D))\\(b:\mycube{l}^{n,p}(D)(E)(d))\end{array} & :      & \!\!\!\begin{array}{ll}\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon',r}{n,p}(D)(d))(\downcube{l,\epsilon',r}{n,p}(D)(E)(d)(b)) \\ \eqett \downcube{l,\epsilon',r}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))(\downcube{l,\epsilon,q+1}{n,p}(D)(E)(d)(b))\end{array}                                                                             \\
          \cohcube{l,\epsilon,\epsilon',q,r}{n,p,[p=r]}                         & D~E~d~(b,\_)                     & \defeq & \reflett(\downcube{l,\epsilon,q-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon',p}{n,p}(D)(d))(b_{\epsilon})) \\
          \cohcube{l,\epsilon,\epsilon',q,r}{n,p,[p<r]}                         & D~E~d~(b,c)                      & \defeq & \!\!\begin{array}{l}(\cohlayer{l,\epsilon,\epsilon',q,r}{n,p}(D)(d)(b),\;\cohcube{l,\epsilon,\epsilon',q,r}{n,p+1}(D)(E)(d,b)(c))\end{array}                                                                               \\
        \end{array}
      $}}
  \caption{Definition of a homogeneous bare cubical set (commutation of $q$-th projection and $r$-th projection)}
  \label{fig:barecubicalsetcoherences}
\end{figure*}

>>>>

\begin{figure*}
  \centerline{ \framebox{$
        \begin{array}{llcl}
          \cohbox{l,\epsilon,\epsilon',q,r}{\!\!\!\begin{array}{l}n,p\\\mbox{}[p \leq r \leq q \leq n - 2]\end{array}}    & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\end{array} & :      & \!\!\!\begin{array}{ll}\downbox{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\epsilon',r}{n,p}(D)(d)) \\ \eqett \downbox{l,\epsilon',r}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))\end{array}                                                                             \\
          \cohbox{l,\epsilon,\epsilon',q,r}{n,0}                                & D~\unitpoint                     & \defeq & \reflett(\unitpoint)                                                                                         \\
          \cohbox{l,\epsilon,\epsilon',q,r}{n,p'+1}                             & D~(d,b)                          & \defeq & (\cohbox{l,\epsilon,\epsilon',q,r}{n,p'}(D)(d),\cohlayer{l,\epsilon,\epsilon',q,r}{n,p'}(D)(d)(b))           \\
          \\
          \cohlayer{l,\epsilon,\epsilon',q,r}{\!\!\!\begin{array}{l}n,p\\\mbox{}[p < r \leq q \leq n - 2]\end{array}} & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(d:\mybox{l}^{n,p}(D))\\(b:\mylayer{l}^{n,p}(D)(d))\end{array} & :      & \!\!\!\begin{array}{ll}\downlayer{l,\epsilon,q}{n-1,p}(\hd(D))(\downbox{l,\epsilon',r}{n,p}(D)(d))(\downlayer{l,\epsilon',r}{n,p}(D)(d)(b)) \\ \eqett \downlayer{l,\epsilon',r}{n-1,p}(\hd(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))(\downlayer{l,\epsilon,q+1}{n,p}(D)(d)(b))\end{array}                                                                             \\
          \cohlayer{l,\epsilon,\epsilon',q,r}{n,p}                              & D~d~c                            & \defeq & \!\!\begin{array}{l}(\cohcube{l,\epsilon,\epsilon',q-1,r-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,L,p}{n,p}(D)(d))(c_L),\\\;\cohcube{l,\epsilon,\epsilon',q-1,r-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,R,p}{n,p}(D)(d))(c_R))\end{array}                                                                               \\
          \\
          \cohcube{l,\epsilon,\epsilon',q,r}{\!\!\!\begin{array}{l}n,p\\\mbox{}[p \leq r \leq q \leq n - 2]\end{array}}  & \!\!\!\begin{array}{l}(D:\partialcubset{l}{n})\\(E:\mycubsetcomp{l}{n}(D))\\(d:\mybox{l}^{n,p}(D))\\(b:\mycube{l}^{n,p}(D)(E)(d))\end{array} & :      & \!\!\!\begin{array}{ll}\downcube{l,\epsilon,q}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon',r}{n,p}(D)(d))(\downcube{l,\epsilon',r}{n,p}(D)(E)(d)(b)) \\ \eqett \downcube{l,\epsilon',r}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon,q+1}{n,p}(D)(d))(\downcube{l,\epsilon,q+1}{n,p}(D)(E)(d)(b))\end{array}                                                                             \\
          \cohcube{l,\epsilon,\epsilon',q,r}{n,p,[p=r]}                         & D~E~d~(b,\_)                     & \defeq & \reflett(\downcube{l,\epsilon,q-1}{n-1,p}(\hd(D))(\tl(D))(\downbox{l,\epsilon',p}{n,p}(D)(d))(b_{\epsilon})) \\
          \cohcube{l,\epsilon,\epsilon',q,r}{n,p,[p<r]}                         & D~E~d~(b,c)                      & \defeq & \!\!\begin{array}{l}(\cohlayer{l,\epsilon,\epsilon',q,r}{n,p}(D)(d)(b),\;\cohcube{l,\epsilon,\epsilon',q,r}{n,p+1}(D)(E)(d,b)(c))\end{array}                                                                               \\
        \end{array}
      $}}
  \caption{Definition of a homogeneous bare cubical set (commutation of $q$-th projection and $r$-th projection)}
  \label{fig:barecubicalsetcoherences}
\end{figure*}
